What We Eval in the Shadows

### 2021-08-09 paper/main.tex
Add do.call and %||%

@@

\subsection{Miscellaneous}

The \code{withr} package provides the \code{defer} function which defers the
evaluation of an expression until a stack frame is exited. It attaches this
expression as an attribute to the frame environment and uses \eval to evaluate
it on frame exit.

>>>>

Similar idea is used by the \code{igraph} package to define the \code{\%\|\|\%}
operator whose code is shown below. This operator returns the result of
evaluating the first argument (\code{lhs}) if it is not \code{NULL}, otherwise
it returns the result of evaluating the second argument (\code{rhs}). This is
similar to the \code{\|\|} operator which performs the logical OR of its
arguments except it treats \code{NULL} as the \code{FALSE} value.

\begin{lstlisting}
`%||%` <- function (lhs, rhs) {
    lres <- withVisible(eval(lhs, envir = parent.frame()))
    if (is.null(lres$value)) {
        eval(rhs, envir = parent.frame())
    } else {
        if (lres$visible) { lres$value}
        else { invisible(lres$value) }
   }
}
\end{lstlisting}

Many packages use \eval to implement variations of the \code{base} R functions.
For example, the \code{igraph} package provides the \code{do_call} function
shown below. This is a variant of the \code{do.call} function from the
\code{base} package. This function executes a function call by constructs it
from a name and a list of arguments and calling \eval.
\begin{lstlisting}
do_call <- function(f, ..., .args = list(), .env = parent.frame()) {
  f <- substitute(f)
  call <- make_call(f, ..., .args)
  eval(call, .env)
}
\end{lstlisting}

@@
